---
title: "CoSIAdata, an Experimental Hub Package of VST Stabilized RNA-Seq Data that accompanies the CoSIA Package"
output: 
  BiocStyle::html_document:
    toc: true
    toc_float: true
    fig_width: 5
    
vignette: >
  %\VignetteIndexEntry{CoSIAdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author: Anisha Haldar, Vishal H. Oza, Amanda D. Clark, Brittany N. Lasseigne
date: 2023-02-13
---

```{css, echo=FALSE}
.row {
  margin-left: -200px;
}
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


**** 
# CoSIAdata Introduction

VST Stabilized RNA-Seq Expression Data from Bgee across six species and more 
than 132 tissues are made available through the CoSIAdata package. 
The six species available through the package are *Homo sapiens*, 
*Mus musculus*, *Rattus norvegicus*, *Danio rerio*, *Drosophila melanogaster*, 
and *Caenorhabditis elegans*. Each species is found in an individualized Rdata 
file from ExperimentHub and can be used in conjunction with CoSIA, a 
visualization tool for comparing across species using gene expression metrics. 
CoSIAdata's individualized datasets provide the Anatomical Entity Name, 
Anatomical Entity Id, Ensembl Id, and Experimental Id to accompany the 
VST Stabilized RNA-Seq Expression Data allowing for species, tissue, and 
gene-specific analysis to be conducted. 

The example below demonstrates the process of downloading these 
datasets from Experimental Hub.

```{r get-CoSIAdata}
library(ExperimentHub)
eh <- ExperimentHub()
query(eh, "CoSIAdata")
```

One can then extract the species specific data.
```{r download-c.elegan_data}
head(eh[["EH7863"]])
```

Session Info
```{r}
sessionInfo()
```

