---
title: "CoSIAdata, an Experimental Hub Package for work with CoSIA"
output: 
  BiocStyle::html_document:
    toc: true
    toc_float: true
    fig_width: 5
    
vignette: >
  %\VignetteIndexEntry{CoSIAdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author: Anisha Haldar, Vishal H. Oza
date: 2023-01-13
---

```{css, echo=FALSE}
.row {
  margin-left: -200px;
}
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


**** 
# add a description about the data package below (sample is added to hold space)

TCGA re-processed RNA-Seq data from 9264 Tumor Samples and 741 normal samples
across 24 cancer types and made it available via [GSE62944](http://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE62944) from GEO.
This data is also available as an ExpressionSet from ExperimentHub and
can be used for Differential Expression Analysis.

In the below example, we show how one can download this dataset from 
ExperimentHub.

```{r get-CoSIAdata}
library(ExperimentHub)
eh = ExperimentHub()
query(eh , "CoSIAdata")
```

One can then extract the data for this using
```{r download-tcga}
tcga_data <- eh[["EH1"]]
```
The different cancer types can be accessed using -

```{r cancer-types}
 head(phenoData(tcga_data)$CancerType)
```
Above we show only the top 6 Cancer subtypes.


